### 2021-05-14 project_ashish_monograph/upgrade.tex
updated
TEPX linearity figures updated

Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$. A Linear relation between the number of clusters and pileup (PU) would imply that\\

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_linearity.png}
  \caption{Simulated mean number of clusters for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_residuals.png}
  \caption{Deviation from linearity for clusters for entire TEPX detector. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value. Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity.png}
  \caption{Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for clusters for TEPX Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_negativez_Linearity.png}
  \caption{Simulated mean number of clusters for -z side TEPX disks as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_negativez_Linearity_residuals.png}
  \caption{Deviation from linearity for clusters for -z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_positivez_linearity.png}
  \caption{Simulated mean number of clusters for +z side TEPX disks as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_postivez_Linearity_residuals.png}
  \caption{Deviation from linearity for clusters for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity.png}
  \caption{Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity_residuals.png}
  \caption{Deviation from linearity for clusters for TEPX Disk 4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector. The non-linearity is calculated as
the relative difference between the data points and the values of the fit function at the respective pileup value.
Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC
environment.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1. The non-linearity is calculated as the
relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity.png}
  \caption{Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
  \caption{Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity.png}
  \caption{Simulated mean number of coincidences in \phi for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity.png}
  \caption{Simulated mean number of coincidences in r for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
  \caption{Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
  \caption{Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

>>>>

Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$. A linear relation between the number of clusters and pileup (PU) would imply that\\

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./totalclusters.png}
  \caption{\onehalfspacing Left: Simulated mean number of clusters for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: Deviation from linearity for clusters for entire TEPX detector. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value. Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./clustersD4R1.png}
  \caption{\onehalfspacing Left: Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./clustersperdisk-z.png}
  \caption{Left: Simulated mean number of clusters for -z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for -z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./clustersperdisk+z.png}
  \caption{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./clustersperringD-4.png}
  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for clusters for TEPX Disk 4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./clustersperringD+4.png}
  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for clusters for TEPX Disk 4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./totalcoincidences.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value. Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC
environment. }
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{.//coincidencesperdisk-z.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesperdisk+z.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinphiD4R1z+.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinrD4R1z+.png}
  \caption{Left: Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD-4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD+4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD-4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}
